Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-07-01 paper/paper.Rmd
minor tweaks

@@

>>>>

Flag: in some cases (auc) we found that the key test statistic was not coded correctly.

@@

```{r}
layout(matrix(1:22,nr=11,byr=T))
for (key in project_plan$project_key) {
  tryCatch(source(function() {
  orig <- readPNG(paste0("figures/",key,"-original.png"))
  rep <- readPNG(paste0("figures/",key,"-replication.png"))
  plot(orig)
  plot(rep)}
  ))
}
```
